%====================
% EXPERIENCE A
%====================
\subsection[A]{Harvard Science Center \hfill Jan 2017 --- Present}
\subtext{The Center for Astrophysics | Harvard \& Smithsonian (CfA) \hfill Cambridge, MA}
\begin{zitemize}
\item Operated and maintained the 0.4 meter Clay Telescope atop the Harvard University Science Center.
\item Hosted star parties and other outreach events for the undergraduate and local community.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection[B]{Graduate student researcher \hfill Sep 2016 --- May 2022}
\subtext{The Center for Astrophysics | Harvard \& Smithsonian (CfA) \hfill Cambridge, MA}
\begin{zitemize}
\item Provided spectroscopic time-series observations and follow-up atmospheric analysis for an underrepresented class of exoplanet.
\item Accomplished this using Gaussian process (GP) and principal component analysis (PCA) detrending techniques, combined with Bayesian inference frameworks including Markov chain Monte Carlo (MCMC) and nested sampling.
\item Utilized high performance computing facilities and schedulers (Torque/PBS, SGE, slurm) via ssh and the command line on different Linux operating systems.
\item Taught/mentored several undergraduate courses in Astronomy and received multiple teaching awards.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection[C]{Co-Instructor \hfill Jun 2017 --- Sep 2019}
\subtext{Banneker Institute \hfill Cambridge, MA}
\begin{zitemize}
\item Collaborated in the design and execution of a novel summer astronomy workshop through the ISEE Professional Development Program geared towards underrepresented students in STEM.
\item Taught 20+ class size emphasizing hands-on and inquiry based learning.
\end{zitemize}